### 2016-03-18 docs/ms_communitySynchrony.Rmd
changes site orders in table to go by species richness

\noindent where $N_i(t)$ is the biomass of species *i* in year *t*, and $r_i(t)$ is its population growth rate in year *t*. 
$r_{mi}$ is species *i*'s intrinsic rate of increase, $K_i$ is its carrying capacity, and $\alpha_{ij}$ is the interspecific competition coefficient representing the effect of species *j* on species *i*. 
Environmental stochasticity is incorporated as $\sigma_{ei}u_{ei}(t)$, where $\sigma_{ei}^2$ is the environmental variance and $u_{ei}$ are normal random variables with zero mean and unit variance that are independent through time but may be correlated between species.
Demographic stochasticity arises from variations in births and deaths among individuals (e.g., same states, different fates), and is included in the model as a first-order, normal approximation [@Lande2003; @DeMazancourt2013a].
$\sigma_{di}^2$ is the demographic variance and $u_{di}(t)$ are independent normal variables with zero mean and unit variance.

To derive analytical predictions we solved a first-order approximation of Equation 2 (Online Supporting Information).

@@

| Site Name | Biome | Location (Lat, Lon) | Obs. Years | Species |
| --------- | ----- | ------------------- | ---------- | ------- |
| Arizona | Sonoran Desert | 31&deg;50' N, 110&deg;53' W | 1915-1933 | *Bouteloua eriopoda* |
| | | | | *Bouteloua rothrockii* |
| Idaho | Sagebrush steppe | 44.2&deg; N, 112.1&deg; W | 1926-1957 | *Artemisia tripartita* |
| | | | | *Pseudoroegneria spicata* |
| | | | | *Hesperostipa comata* |
| | | | | *Poa secunda* |
| Kansas | Southern mixed prairie | 38.8&deg; N, 99.3&deg; W | 1932-1972 | *Bouteloua curtipendula* |
| | | | | *Bouteloua hirsuta* |
| | | | | *Schizachyrium scoparium* |
| Montana | Northern mixed prairie | 46&deg;19' N, 105&deg;48' W | 1926-1957 | *Bouteloua gracilis* |
| | | | | *Hesperostipa comata* |
| | | | | *Pascopyrum smithii* |
| | | | | *Poa secunda* |
| New Mexico | Chihuahuan Desert | 32.62&deg; N, 106.67&deg; W | 1915-1950 | *Bouteloua eriopoda* |
| | | | | *Sporobolus flexuosus* |

@@

table_data <- alltable_data[,c("Site", "V1", "V4", "V7")]
table_data$spp <- c(length(unique(az_data$species)),
                    length(unique(id_data$species)),
                    length(unique(ks_data$species)),
                    length(unique(mt_data$species)),
                    length(unique(nm_data$species)))
colnames(table_data) <- c("Site",
                          "$\\phi_{R}$", 
                          "$\\phi_{C}$",
                          "CV of Total Cover",
                          "Species richness")
# colnames(table_data) <- c("Site",
#                           "$\\phi_{r}$", 
#                           "$\\text{E}(\\phi_{r})$", 
#                           "$\\text{E}(\\sigma_{r,c} + \\sigma_{r,e})$",
#                           "$\\phi_{C}$", 
#                           "$\\text{E}(\\phi_{C})$",
#                           "$\\text{E}(\\sigma_{C,c} + \\sigma_{C,e})$",
#                           "CV of Total Cover",
#                           "Species richness")
# table_data[,3] <- round(1/table_data[,ncol(table_data)],2) # reset expected sybchrony to 1/S
# table_data[,4] <- table_data[,2] - table_data[,3] # calculate obs - exp synchrony

synch_cap <- "Observed synchrony among species' per capita growth rates ($\\phi_{r}$), observed synchrony among species' percent cover ($\\phi_{C}$), the coefficient of variation of total community cover, and species richness for each community. Species richness values reflect the number of species analyzed from the community, not the actual richness."
print(xtable(table_data, caption = synch_cap),
      caption.placement="top",
      include.rownames = F, 
      sanitize.colnames.function = identity,
      comment=FALSE,
      size="normalsize")
```

@@

```{r prediction_table, echo=FALSE, include=TRUE, results='asis', message=FALSE, eval=F, cache=FALSE}
exp_synchrony_env <- readRDS("../results/envstoch_predictions.RDS")
exp_synchrony_env <- exp_synchrony_env[complete.cases(exp_synchrony_env),]
exp_synchrony_demo <- alltable_data[,c("V2","V5")]
exp_synchrony_demo$site <- table_data$Site
colnames(exp_synchrony_demo) <- c("pgr", "cover", "site")
sims_output <- readRDS("../results/allsims_plot_data.RDS")

@@

pred_cap <- "Comparisons between our analytical predictions and simulation results for synchrony of species' per capita growth rates. Analytical predictions represent two limiting cases where only demographic stochasticity is operating ($\\phi_{R,\\mathcal{M}_D}$) and where only environmental stochasticity is operating ($\\phi_{R,\\mathcal{M}_E}$). Simulated synchrony values come from our empirically-based, multi-species population models when simulated under conditions that match the limiting case conditions (e.g., environmental stochasticity and competition removed for $\\mathcal{M}_D$)."
print(xtable(pred_table, caption = pred_cap),
      caption.placement="top",
      include.rownames = F, 
      sanitize.colnames.function = identity,
      comment=FALSE,
      size="normalsize")
```

>>>>

\noindent where $N_i(t)$ is the biomass of species *i* in year *t*, and $r_i(t)$ is its population growth rate in year *t*. 
$r_{mi}$ is species *i*'s intrinsic rate of increase, $K_i$ is its carrying capacity, and $\alpha_{ij}$ is the interspecific competition coefficient representing the effect of species *j* on species *i*. 
Environmental stochasticity is incorporated as $\sigma_{ei}u_{ei}(t)$, where $\sigma_{ei}^2$ is the environmental variance and $u_{ei}$ are normal random variables with zero mean and unit variance that are independent through time but may be correlated between species.
Demographic stochasticity arises from variations in births and deaths among individuals (e.g., same states, different fates), and is included in the model as a first-order, normal approximation [@Lande2003; @DeMazancourt2013a].
$\sigma_{di}^2$ is the demographic variance and $u_{di}(t)$ are independent normal variables with zero mean and unit variance.
To derive analytical predictions we solved a first-order approximation of Equation 2 [@DeMazancourt2013a and Online Supporting Information].

@@

| Site Name | Biome | Location (Lat, Lon) | Obs. Years | Species |
| --------- | ----- | ------------------- | ---------- | ------- |
| New Mexico | Chihuahuan Desert | 32.62&deg; N, 106.67&deg; W | 1915-1950 | *Bouteloua eriopoda* |
| | | | | *Sporobolus flexuosus* |
| Arizona | Sonoran Desert | 31&deg;50' N, 110&deg;53' W | 1915-1933 | *Bouteloua eriopoda* |
| | | | | *Bouteloua rothrockii* |
| Kansas | Southern mixed prairie | 38.8&deg; N, 99.3&deg; W | 1932-1972 | *Bouteloua curtipendula* |
| | | | | *Bouteloua hirsuta* |
| | | | | *Schizachyrium scoparium* |
| Montana | Northern mixed prairie | 46&deg;19' N, 105&deg;48' W | 1926-1957 | *Bouteloua gracilis* |
| | | | | *Hesperostipa comata* |
| | | | | *Pascopyrum smithii* |
| | | | | *Poa secunda* |
| Idaho | Sagebrush steppe | 44.2&deg; N, 112.1&deg; W | 1926-1957 | *Artemisia tripartita* |
| | | | | *Pseudoroegneria spicata* |
| | | | | *Hesperostipa comata* |
| | | | | *Poa secunda* |

@@

table_data <- alltable_data[,c("Site", "V1", "V4", "V7")]
table_data$spp <- c(length(unique(az_data$species)),
                    length(unique(id_data$species)),
                    length(unique(ks_data$species)),
                    length(unique(mt_data$species)),
                    length(unique(nm_data$species)))
colnames(table_data) <- c("Site",
                          "$\\phi_{R}$", 
                          "$\\phi_{C}$",
                          "CV of Total Cover",
                          "Species richness")
myorder <- c(5,1,3,4,2)
xtable_data <- table_data[myorder,]
# colnames(table_data) <- c("Site",
#                           "$\\phi_{r}$", 
#                           "$\\text{E}(\\phi_{r})$", 
#                           "$\\text{E}(\\sigma_{r,c} + \\sigma_{r,e})$",
#                           "$\\phi_{C}$", 
#                           "$\\text{E}(\\phi_{C})$",
#                           "$\\text{E}(\\sigma_{C,c} + \\sigma_{C,e})$",
#                           "CV of Total Cover",
#                           "Species richness")
# table_data[,3] <- round(1/table_data[,ncol(table_data)],2) # reset expected sybchrony to 1/S
# table_data[,4] <- table_data[,2] - table_data[,3] # calculate obs - exp synchrony

synch_cap <- "Observed synchrony among species' per capita growth rates ($\\phi_{r}$), observed synchrony among species' percent cover ($\\phi_{C}$), the coefficient of variation of total community cover, and species richness for each community. Species richness values reflect the number of species analyzed from the community, not the actual richness."
print(xtable(xtable_data, caption = synch_cap),
      caption.placement="top",
      include.rownames = F, 
      sanitize.colnames.function = identity,
      comment=FALSE,
      size="normalsize")
```

@@

```{r prediction_table, echo=FALSE, include=TRUE, results='asis', message=FALSE, eval=T, cache=FALSE}
exp_synchrony_env <- readRDS("../results/envstoch_predictions.RDS")
exp_synchrony_env <- exp_synchrony_env[complete.cases(exp_synchrony_env),]
exp_synchrony_demo <- alltable_data[,c("V2","V5")]
exp_synchrony_demo$site <- table_data$Site
colnames(exp_synchrony_demo) <- c("pgr", "cover", "site")
sims_output <- readRDS("../results/allsims_plot_data.RDS")

@@

myorder <- c(5,1,3,4,2)
xpred_table <- pred_table[myorder,]
pred_cap <- "Comparisons between our analytical predictions and simulation results for synchrony of species' per capita growth rates. Analytical predictions represent two limiting cases where only demographic stochasticity is operating ($\\phi_{R,\\mathcal{M}_D}$) and where only environmental stochasticity is operating ($\\phi_{R,\\mathcal{M}_E}$). Simulated synchrony values come from our empirically-based, multi-species population models when simulated under conditions that match the limiting case conditions (e.g., environmental stochasticity and competition removed for $\\mathcal{M}_D$)."
print(xtable(xpred_table, caption = pred_cap),
      caption.placement="top",
      include.rownames = F, 
      sanitize.colnames.function = identity,
      comment=FALSE,
      size="normalsize")
```
